Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
deplacement + check anglais du paragraphe sur le choix de sigma

\MM{Je trouve ça assez frustrant d'arriver ici et de ne toujours pas
  savoir quel $\sigma$ est choisi. A mon avis, on peut remonter la
  description du $\sigma$ dynamique de la section suivante à ici. Ça
  évite de le présenter comme un petit détail d'implémentation alors
  que c'est quand même une vraie contrib par rapport au papier
  original.}

@@

\MM{cf. ci-dessus, j'aurais mis ça dans la section invariants
  disjonctifs}
For the computation of disjunctive invariants, we experimented with a heuristic
of dynamic construction of the $\sigma$ function, adapted from
\cite{DBLP:conf/pldi/GulwaniZ10}.  We start with one single
disjunct per control point ($m=1$), and we start with an empty map $\sigma$. We also
define a maximal bound on the number of disjunct per control point, noted $M$.
$\sigma(j,k)$ is then constructed on the fly only when needed.
When $\sigma(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_k$ by the path indexed by $j$, and try to find an existing
disjunct of index $k'$ so that the least upper bound of the two abstract values is
exactly the union of them. If such an index exists, then we set $\sigma(j,k) = k'$.
Otherwise:
\begin{itemize}
	\item if $m < M$, we increase $m$ by $1$ and define $\sigma(j,k) = m$
	\item if $m = M$, we define $\sigma(j,k) = M$
\end{itemize}

>>>>

We experimented with a heuristic
of dynamic construction of the $\sigma$ function, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
We start with one single
disjunct per control point ($m=1$) and an empty map $\sigma$.
$M$ denotes an upper bound on the number of disjuncts per control point.
$\sigma(j,k)$ is then constructed on the fly only when needed.
When $\sigma(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_k$ by the path indexed by $j$, and try to find an existing
disjunct of index $k'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma(j,k) = k'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m < M$, we increase $m$ by $1$ and define $\sigma(j,k) = m$
	\item if $m = M$, we define $\sigma(j,k) = M$
\end{itemize}

@@
